Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2018-03-11 QPQ9/Submit/qpq9_resubmit_4.tex
Addressed fourth referee report.

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}.
{\bf We find that the mean absorptions exhibit large velocity widths
$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems.
We find the observed widths are consistent with gas in gravitational
motion and Hubble flow. However, while the observation of large widths alone does not require
galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
is anisotropic or intermittent.}
\end{abstract}

@@

Direct observations of galactic flows are difficult to acquire. Detecting the presence of
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are
accentuated for distant, young galaxies, where flows of gas are predicted to prevail
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions,
\citep[e.g.][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we
measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the
circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic
redshift.
{\bf From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
systems, we measured the velocity interval that encompasses 90\% of the total optical depth,
$\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is
$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for
\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed
all previous measurements from galaxies and/or absorption systems at any epoch.
The offsets, $\delta v$, are often positive, with the sign convention that positive
velocities indicate a redshift from the systemic.
}

With absorption-line spectroscopy of background sightlines, other researchers also have had
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial
velocity, with quasar-driven outflows being one possible explanation. However, we consider that
their velocity spreads can be better quantified. Other
existing studies that found large velocity spreads are {\bf single sightlines
\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}}, or with gas tracing
a higher ionization state than the QPQ absorption systems \citep[e.g.,][]{Churchill+12}, or where
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller
than that of QPQ8.

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin,
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue.
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is
included in the modeling. The absorptions frequently exhibit large velocity widths. The blue dashed
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The
$1\sigma$ modeling error for the
{\bf dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
$25\,{\rm km\,s^{-1}}$ respectively, which are}
also the typical modeling errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

@@

Visually, there are two absorption components. One component is the uniform depression in the
continuum level in the stack resulting from absorbers unassociated with the foreground
quasars. The other component comes from absorbers associated with the foreground quasars and
distribute around their systemic velocities. To model the absorption, we introduce
a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.
We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
to the data, we measure
{\bf the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
\ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$. The dispersion suggests extreme kinematics, while
the centroid suggests an asymmetry that contradicts the standard expectation.}
The median
stack, on the other hand, shows weaker absorption,
{\bf and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.}

To test whether the dispersion in the average absorption associated with the foreground quasars is
well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
window surrounding the absorption centroid, while fitting a continuum to the rest of the
$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
One may also speculate on the existence of a broader absorption component hidden in the depressed
continuum. We try replacing the constant absorption component with a broad Gaussian component in our
modeling. We find that this second Gaussian component has
{\bf an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider}
than the entire velocity window for stacking.
This weak and very broad component has no effect on the {\bf width and the centroid} of the narrow,
associated Gaussian component. We therefore consider that one single Gaussian component is a good
description of the average absorption associated with the foreground quasars.
Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
the foreground quasars, and hence will not affect the average absorption measured for the foreground
quasars. Their contribution to the average absorption should result in a tilt in the
pseudo-continuum, which is insignificant.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has
{\bf a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$},
consistent with the full sample.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
{\bf We overplot in dashed, limegreen an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dot dashed, limegreen an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observed width.
In thick, green, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, and broadened
by the mean redshift error in the data. While this model has a dispersion within modeling error of the
dispersion in the data. the centroid of the stack of the data appears to be redshifted
from the systemic. A model with only gravitational motions and Hubble flows cannot explain
this putative asymmetry.}
}
\label{fig:monte}
\end{figure}

@@

{\bf To assess the statistical significance of the observed dispersion, we perform a bootstrap
analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption
profile to model each bootstrap realization. We find that} a width of
$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter in
the bootstrap realizations
(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.

@@

In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian
absorption model of the Monte Carlo simulations.
{\bf In the figure, the Gaussian absorption model is
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.}
The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$,
about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
stack of the sub-sample with [\ion{O}{3}] redshifts as well.
{\bf One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
velocities that are typical for quasar-mass halos, and adopt a different $\sigma_{\rm rms}$ accordingly.
The best-studied coeval, more typical star-forming
galaxies are the Lyman-break galaxies. Their clustering strength implies a characteristic halo
mass of $M_{\rm halo}\approx10^{11.6}\,M/{\rm M_\odot}$ \citep{Bielby+13,Malkan+17}, corresponding to
$\sigma_{\rm rms}=114\,{\rm km\,s^{-1}}$.
If we adopt this smaller $\sigma_{\rm rms}$ insead,for absorbers outside the loosely
defined quasar CGM boundary, at $\gtrsim300$\,kpc, the stack of mock spectra will have a $1\sigma$
dispersion of $247\,{\rm km\,s^{-1}}$. This is again within modeling errors of the observed intrinsic
dispersion.}
We also test for the
sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering
analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$
sightline may in fact intercept more than one optically thick absorber. We double the number of
absorbers for each mock sightline, and find the measured dispersion only increases by several
${\rm km\,s^{-1}}$. Thus, before the putative asymmetry is confirmed, the hypothesis that the
observed velocity width is only produced by a
combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical
processes are not necessary to explain the large velocity fields.

@@

{\bf We quote} the standard deviation in the bootstrap
realizations to be the scatter in the centroids of the data. The scatters
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
absorption.

One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2}\,1334, absorption from \ion{C}{2*}\,1335
would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334.
{\bf Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.}
Among these nine subsystems, only one,
labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
{\bf We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
$\approx+40\,{\rm km\,s^{-1}}$.}
Hence, contamination from \ion{C}{2*}\,1335 could not be responsible for the observed redshift in
the centroid.

@@

Since the large scatter in the centroids represents intrinsic variation rather than redshift
errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we consider
that
{\bf systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.}
%the asymmetry signal in the $z\sim2$ sample is likely to be real.
In the Discussion section, we discuss two possible explanations for the asymmetry.

@@

In the following, we explore two possible explanations for the {\bf non-dynamical processes} that
provides the {\bf putative asymmetry}.
The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
opacity in background sightlines passing close to foreground quasars.

@@

Another possible explanation arises from the finite lifetime of quasar episodes.
Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. The light from
the background quasar may arrive at the gas behind
the foreground quasar before the ionizing radiation from the foreground quasar arrives. In
QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average
extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
$\sim10^6$\,yr.
In turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
constraints from
observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.

The first explanation above to asymmetric
absorption requires that the quasars emit their ionizing radiation anisotropically, while the
second explanation requires the quasars emit their ionizing radiation intermittently. Both
explanations will require the line-of-sight motions of the gas to be {\bf not in a net inflow.}
Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate ion, and a
blueshifted absorption signal needs to be searched in a higher ion.

{\bf We test the case of Hubble flows versus galactic-scale outflows in producing the putative
asymmetry. We try implementing an arbitrary quasar opening angle in our Monte Carlo simulations to
reproduce an absorption centroid that is redshifted from the systemic. In QPQ6, we argued that
the observed anisotropic clustering of optically thick systems around quasars demands that a quasar's
radiation field must affect optically thick systems on Mpc scales. Hence in this test, we set the
incidence of absorbers happening within the quasar opening angle to be zero, for absorbers at all
disances from the quasar. In the case without
outflows, even if we set the opening angle to be $180^\circ$, i.e. absorption only happens at
positive velocities, the mean absorption centroid would merely reach $\approx+85\,{\rm km\,s^{-1}}$.
Hence, the observed $\delta v\approx+200\,{\rm km\,s^{-1}}$ shift in the mean absorption cannot be
produced by asymmetric distribution in Hubble velocities alone. This suggests the presence of an
outflow component to account for extra asymmetry in line-of-sight velocities.
We crudely estimate that, for an opening angle of $120^\circ$ and radial outflows at
velocities $\approx500\,{\rm km\,s^{-1}}$, our Monte Carlo simulations may reproduce the
observed centroid and intrinsic dispersion of the mean absorption by \ion{C}{2}.}

>>>>

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$.
We employ 148 projected quasar pairs to study the circumgalactic gas of the foreground quasars in
absorption. The sample selects foreground quasars with precise redshift measurements, using
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4},
and \ion{Mg}{2}.
We find that the mean absorptions exhibit large velocity widths
$\sigma_v\approx300\,{\rm km\,s^{-1}}$. Further, the mean absorptions appear to be asymmetric about
the systemic redshifts. The mean absorption centroids exhibit small redshift relative to the
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid
velocities of the individual absorption systems.
We find the observed widths are consistent with gas in gravitational
motion and Hubble flow. However, while the observation of large widths alone does not require
galactic-scale outflows, the observed offsets suggest that the gas is on average outflowing from the
galaxy. The observed offsets also suggest that the ionizing radiation from the foreground quasars
is anisotropic {\bf and/or} intermittent.
\end{abstract}

@@

Direct observations of galactic flows are difficult to acquire. Detecting the presence of
the gas is itself challenging. Either the gas mass is too small, or the gas density is too low for
the detection of line-emission, e.g.\ 21\,cm, Ly$\alpha$, or H$\alpha$ from \ion{H}{1}. Resolving
the kinematics and establishing the mass flux pose an even greater challenge. These challenges are
accentuated for distant, young galaxies, where flows of gas are predicted to prevail
\citep{Keres+09,Fumagalli+11}. Therefore, with rare exceptions,
\citep[e.g.,][]{Cantalupo+14,Hennawi+15}, the community has relied on absorption-line spectroscopy
to detect and characterize the gas surrounding galaxies
\citep[e.g.,][]{BergeronBoisse91,Steidel+10,Prochaska+11,Tumlinson+13}.
In a previous paper of the Qussars Probing Quasars series \citep[][, hereafter QPQ8]{QPQ8}, we
measured the velocity field for \ion{C}{2}\,1334 and \ion{C}{4}\,1548, finding that the
circumgalactic medium frequently exhibits large velocity widths that are offset from the systemic
redshift.
From a sample of 7 \ion{C}{2} systems and 10 \ion{C}{4}
systems, we measured the velocity interval that encompasses 90\% of the total optical depth,
$\Delta v_{90}$, and the $1\sigma$ dispersion relative to the profile centroid, $\sigma_v$.
The median $\Delta v_{90}$ is $555\,{\rm km\,s^{-1}}$ for \ion{C}{2}\,1334 and is
$342\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. The median $\sigma_v$ is $249\,{\rm km\,s^{-1}}$ for
\ion{C}{2}\,1334 and is $495\,{\rm km\,s^{-1}}$ for \ion{C}{4}\,1548. These velocity fields exceed
all previous measurements from galaxies and/or absorption systems at any epoch.
The offsets, $\delta v$, are often positive, with the sign convention that positive
velocities indicate a redshift from the systemic.

With absorption-line spectroscopy of background sightlines, other researchers also have had
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial
velocity, with quasar-driven outflows being one possible explanation. However, we consider that
their velocity spreads can be better quantified. Other
existing studies that found large velocity spreads are single sightlines
\citep[e.g.,][]{Tripp+11,RudieNewmanMurphy17}, or with gas tracing
a higher ionization state than the QPQ absorption systems \citep[e.g.,][]{Churchill+12}, or where
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier13}, where a
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller
than that of QPQ8.

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin,
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue.
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is
included in the modeling. The absorptions frequently exhibit large velocity widths. The blue dashed
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The
$1\sigma$ modeling error for the
dispersion and the centroid of the \ion{C}{2} mean stack are $27\,{\rm km\,s^{-1}}$ and
$25\,{\rm km\,s^{-1}}$ respectively, which are}
also the typical modeling errors of the other stacks.
\label{fig:stacks_and_fits}
\end{figure}

@@

Visually, there are two absorption components. One component is the uniform depression in the
continuum level in the stack resulting from absorbers unassociated with the foreground
quasars. The other component comes from absorbers associated with the foreground quasars and
distribute around their systemic velocities. To model the absorption, we introduce
a Gaussian profile while allowing a constant ``pseudo-continuum'' to vary.
We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit
to the data, we measure
the $1\sigma$ dispersion of the stack to be $293\,{\rm km\,s^{-1}}$ and the centroid of the
\ion{C}{2} stack to be $+232\,{\rm km\,s^{-1}}$. The dispersion suggests extreme kinematics, while
the centroid suggests an asymmetry that contradicts the standard expectation.
The median
stack, on the other hand, shows weaker absorption,
and the Gaussian model has a more uncertain dispersion and a centroid with smaller offset.

To test whether the dispersion in the average absorption associated with the foreground quasars is
well-captured by a Gaussian model, we also calculate the dispersion separately using the standard
deviation formula. Specifically, we apply the standard deviation formula to a $\pm1300\,{\rm km\,s^{-1}}$
window surrounding the absorption centroid, while fitting a continuum to the rest of the
$\pm3000\,{\rm km\,s^{-1}}$ window for stacking. The
dispersion measured with the above method is essentially the same as that found by fitting a Gaussian.
One may also speculate on the existence of a broader absorption component hidden in the depressed
continuum. We try replacing the constant absorption component with a broad Gaussian component in our
modeling. We find that this second Gaussian component has
an amplitude of $0.030\pm0.009$, i.e.\ essentially the same amplitude as the initial
constant absorption component, and a $1\sigma$ dispersion of $3614\pm1731\,{\rm km\,s^{-1}}$, i.e.\ wider
than the entire velocity window for stacking.
This weak and very broad component has no effect on the width and the centroid of the narrow,
associated Gaussian component. We therefore consider that one single Gaussian component is a good
description of the average absorption associated with the foreground quasars.
Moreover, narrow associated absorbers of background quasars will not prefer the systemic velocities of
the foreground quasars, and hence will not affect the average absorption measured for the foreground
quasars. Their contribution to the average absorption should result in a tilt in the
pseudo-continuum, which is insignificant.

We also create mean and median stack for the sub-sample with [\ion{O}{3}] redshifts and model the
absorption with Gaussian best-fit. The \ion{C}{2} mean stack for this sub-sample has
a dispersion of $330\,{\rm km\,s^{-1}}$, and a centroid at $+235\,{\rm km\,s^{-1}}$,
consistent with the full sample.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
We overplot in dashed, limegreen an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dot dashed, limegreen an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observed width.
In thick, green, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, and broadened
by the mean redshift error in the data. While this model has a dispersion within modeling error of the
dispersion in the data. the centroid of the stack of the data appears to be redshifted
from the systemic. A model with only gravitational motions and Hubble flows cannot explain
this putative asymmetry.
}
\label{fig:monte}
\end{figure}

@@

To assess the statistical significance of the observed dispersion, we perform a bootstrap
analysis by randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption
profile to model each bootstrap realization. We find that a width of
$\sigma_v>554\,{\rm km\,s^{-1}}$ would be larger than the observed by three times the scatter in
the bootstrap realizations
(overplotted in Figure~\ref{fig:monte}). In other words, taking into account the redshift errors,
motions in addition to gravitational and Hubble flows that will produce an intrinsic dispersion
$\sigma_v>521\,{\rm km\,s^{-1}}$ can be ruled out.

@@

In Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian
absorption model of the Monte Carlo simulations.
n the figure, the Gaussian absorption model is
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model.
The resulting stack of mock spectra has a $1\sigma$ dispersion of $282\,{\rm km\,s^{-1}}$,
about 2 times the modeling error away from the intrinsic dispersion in the \ion{C}{2} mean stack
for the full sample, and about 2 times the modeling error away from the intrinsic dispersion in the
stack of the sub-sample with [\ion{O}{3}] redshifts as well.
One may also consider whether absorbers in Hubble flow and cosmological distances show peculiar
velocities that are typical for quasar-mass halos, and adopt a different $\sigma_{\rm rms}$ accordingly.
The best-studied coeval, more typical star-forming
galaxies are the Lyman-break galaxies. Their clustering strength implies a characteristic halo
mass of $M_{\rm halo}\approx10^{11.6}\,M/{\rm M_\odot}$ \citep{Bielby+13,Malkan+17}, corresponding to
$\sigma_{\rm rms}=114\,{\rm km\,s^{-1}}$.
If we adopt this smaller $\sigma_{\rm rms}$ insead,for absorbers outside the loosely
defined quasar CGM boundary, at $\gtrsim300$\,kpc, the stack of mock spectra will have a $1\sigma$
dispersion of $247\,{\rm km\,s^{-1}}$. This is again within modeling errors of the observed intrinsic
dispersion.
We also test for the
sensitivity of this measured dispersion to the correlation functions adopted. The QPQ6 clustering
analysis is performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$
sightline may in fact intercept more than one optically thick absorber. We double the number of
absorbers for each mock sightline, and find the measured dispersion only increases by several
${\rm km\,s^{-1}}$. Thus, before the putative asymmetry is confirmed, the hypothesis that the
observed velocity width is only produced by a
combination of gravitational motions and Hubble flows cannot be ruled out. Extra dynamical
processes are not necessary to explain the large velocity fields.

@@

We quote the standard deviation in the bootstrap
realizations to be the scatter in the centroids of the data. The scatters
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We
find that 97\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at
$\delta v<+526\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2}
absorption.

One may ask whether absorption from \ion{C}{2*}\,1335 may bias the measurement of the
\ion{C}{2}\,1334 velocity centroid. In the stacks at \ion{C}{2}\,1334, absorption from \ion{C}{2*}\,1335
would manifest as a component redshifted by $+264\,{\rm km\,s^{-1}}$.
In the higher resolution data from QPQ8, we identify nine \ion{C}{2}-bearing subsystems where absorption
from \ion{C}{2*}\,1335 is not blended with \ion{C}{2}\,1334.
Their mean \ion{C}{2} to \ion{C}{2*} equivalent width ratio is 0.2.
Among these nine subsystems, only one,
labeled J1420+1603F in QPQ8, has a \ion{C}{2*}\,1335 equivalent width comparable to \ion{C}{2}\,1334.
We simulate that absorption from \ion{C}{2*} may only bias the \ion{C}{2} centroid by
$\approx+40\,{\rm km\,s^{-1}}$.
Hence, contamination from \ion{C}{2*}\,1335 could not be responsible for the observed redshift in
the centroid.

@@

Since the large scatter in the centroids represents intrinsic variation rather than redshift
errors, and the \ion{Mg}{2} stack for lower redshift suggests a different centroid, we consider
that
systematic biases are unlikely to explain the asymmetry signal in the $z\sim2$ sample.
%the asymmetry signal in the $z\sim2$ sample is likely to be real.
In the Discussion section, we discuss two possible explanations for the asymmetry.

@@

In the following, we explore two possible explanations for the non-dynamical processes that
provides the putative asymmetry.
The explanations arise from a transverse proximity effect (QPQ4), which is the suppression of
opacity in background sightlines passing close to foreground quasars.

@@

Another possible explanation arises from the finite lifetime of quasar episodes.
Figure~\ref{fig:lighttravel} presents a cartoon for a light travel time argument. The light from
the background quasar may arrive at the gas behind
the foreground quasar before the ionizing radiation from the foreground quasar arrives.

%In
%QPQ7 and QPQ8, we reported that the enhancement in metal ion absorption relative to IGM average
%extends to at least $\approx200$\,kpc. This distance corresponds to a light travelling time of
%$\sim10^6$\,yr.
%n turn, this implies a minimum quasar lifetime of $10^6$\,yr, which lies within existing
%constraints from
%observations \citep[e.g.][]{Martini04} and simulations \citep[e.g.][]{Hopkins+05}.

The first explanation above to asymmetric
absorption requires that the quasars emit their ionizing radiation anisotropically, while the
second explanation requires the quasars emit their ionizing radiation intermittently. Both
explanations will require the line-of-sight motions of the gas to be not in a net inflow.
Were the gas flowing into the galaxy instead, the velocity centroid would be negative.
Under both scenarios, lows ions should be redshifted while high ions should be blueshifted.
Using Cloud photoionization models, we find that, for the typical quasar luminosity of our sample,
a CGM gas that is directly illuminated is highly ionized and shows only marginally detectable
\ion{C}{4} absorption. The redshifted \ion{C}{4} may be regarded as an intermediate ion, and a
blueshifted absorption signal needs to be searched in a higher ion.
